rdatacite
=========

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/rdatacite)](https://cranchecks.info/pkgs/rdatacite)
[![Build Status](https://travis-ci.org/ropensci/rdatacite.svg?branch=master)](https://travis-ci.org/ropensci/rdatacite)
[![codecov.io](https://codecov.io/github/ropensci/rdatacite/coverage.svg?branch=master)](https://codecov.io/github/ropensci/rdatacite?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/rdatacite)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/rdatacite)](https://cran.r-project.org/package=rdatacite)
[![DOI](https://zenodo.org/badge/2521192.svg)](https://zenodo.org/badge/latestdoi/2521192)

`rdatacite` provides programmatic accesses to DataCite (https://datacite.org/) metadata

* REST API. Docs: https://support.datacite.org/docs/api and https://support.datacite.org/reference

`rdatacite` docs: https://docs.ropensci.org/rdatacite

Package API:

```{r echo=FALSE, comment=NA, results='asis'}
cat(paste(" -", paste(sprintf("`%s`", getNamespaceExports("rdatacite")), collapse = "\n - ")))
```

## Installation

Stable CRAN version

```{r eval=FALSE}
install.packages("rdatacite")
```

Development version from github

```{r eval=FALSE}
devtools::install_github("ropensci/rdatacite")
```

```{r}
library('rdatacite')
```

## Result objects

Outputs from nearly all `rdatacite` functions will be of class `dc`, an S3 class that's 
simply a named list of results. You can easily remove the class via `unclass()`.
The `print.dc` method prints the data.frame for the `data`, `included`, and `reports`
slots if they exist, but hides the `meta` named list. You can get to the metadata by
indexing to it like `$meta`.

## Searching

You may want to start with `dc_dois()`.

```{r}
dc_dois(query = "climate change")
```

The `query` parameter supports Elasticearch query string queries. Some examples:

```{r eval=FALSE}
# search within a field
dc_dois(query = "publicationYear:2016")
# fuzzy search (via *) on a nested field
dc_dois(query = "creators.familyName:mil*")
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/rdatacite/issues).
* License: MIT
* Get citation information for `rdatacite` in R doing `citation(package = 'rdatacite')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.
